---
title: "Midterm"
author: "Me"
date: "10/8/2021"
output: 
  html_document:
    toc: true
    theme: united
---


## Project Description

This project is...

The following libraries are needed in for this model:

library(tidyverse)
library(tidycensus)
library(sf)
library(spdep)
library(caret)
library(ckanr)
library(FNN)
library(grid)
library(gridExtra)
library(ggcorrplot)
library(kableExtra)
library(jtools) 
library(ggstance) 
library(stargazer)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Libraries needed for this exercise
library(tidyverse)
library(tidycensus)
library(sf)
library(spdep)
library(caret)
library(ckanr)
library(FNN)
library(grid)
library(gridExtra)
library(ggcorrplot)
library(kableExtra)
library(jtools)     # for regression model plots
library(ggstance) 
library(stargazer)

# Functions and data directory
root.dir = "https://raw.githubusercontent.com/veronicaUPenn22/Public-Policy-Analytics-Landing/master/DATA/"

source("https://raw.githubusercontent.com/veronicaUPenn22/Public-Policy-Analytics-Landing/master/functions.r")

# Color palette
palette5 <- c("#ffcdb2","#ffb4a2","#e5989b","#b5838d","#6d6875")

```

### Data Gathering Methods

For this project, we used the following data sets:

| Dataset        | Description    | Open Data URL  | File Type | Location |
| :------------- | :------------- | :------------- | :------------- | :------------- |
| Boulder County Municipalities | Boundaries polygons | https://opendata-bouldercounty.hub.arcgis.com/datasets/bouldercounty::municipalities/about | geojson | MUSA-508/Midterm |
| Boulder County Boundary | Boundary polygon | https://opendata-bouldercounty.hub.arcgis.com/datasets/county-boundary/explore?location=40.088157%2C-105.373097%2C11.58 | geojson | MUSA-508/Midterm |
| Boulder County Open Spaces | Boundaries for parks and open spaces state and municipally owned | https://opendata-bouldercounty.hub.arcgis.com/datasets/county-open-space/explore?location=40.080100%2C-105.341850%2C11.48&showTable=true | geojson | MUSA-508/Midterm |
| Roads | Boulder County main freeways and road network | https://opendata.arcgis.com/datasets/f8292cbf379e4df7b9b8f62e21120ea7_0.geojson | geojson | "" |



| Student Data | Homes data for Boulder County (2019-2021) | Provided by MUSA508 instructors | geojson | MUSA-508/Midterm |


```{r}

```


### Boulder Data and Homes Data 

```{r cars}

# Load census API key
census_api_key("7fcf0c60997f4d8ccd298e26df0b2f35dc033150",install=TRUE, overwrite=TRUE)

muni <- 
  st_read("~/CPLNPennDesign/590-Musa/Musa508-Vero/MUSA-508/Midterm/Municipalities.geojson") %>%
  st_transform('ESRI:102653')

studentData <- 
  st_read("~/CPLNPennDesign/590-Musa/Musa508-Vero/MUSA-508/Midterm/studentData.geojson", crs = 'ESRI:102254') %>%
  st_transform('ESRI:102653')

boulderCounty <-
  st_read("~/CPLNPennDesign/590-Musa/Musa508-Vero/MUSA-508/Midterm/County_Boundary.geojson")%>%
  st_transform('ESRI:102653')

boulder.sf <- studentData %>%
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326, agr = "constant") %>%
  st_transform('ESRI:102653') %>%
  mutate(TotalBathrooms = nbrThreeQtrBaths + nbrFullBaths + nbrHalfBaths) %>%
  rename(Size = TotalFinishedSF, 
         TotalBedrooms = nbrBedRoom, 
         GarageSize = carStorageSF)


#State Plane Colorado - ESRI:102653
#Colorado North - ESRI:102253
#Colorado Central - ESRI:102254
#Boulder - SR-ORG:7992  

```

### Mappring the dependent variable: price

The following map shows home prices spatially distributed across Boulder County.

```{r Price Map, echo=FALSE, message=FALSE, warning=FALSE}

ggplot() +
  geom_sf(data = boulderCounty, fill = "grey90") +
  geom_sf(data = muni, fill = NA) +
  geom_sf(data = boulder.sf, aes(colour = q5(price)), 
          show.legend = "point", size = .5) +
  scale_color_manual(values = palette5,
                   labels = qBr(boulder.sf, "price"),
                   name = "Quintile\nBreaks") +
  geom_sf_label(data = muni, aes(label = ZONEDESC), size = 2) +
  labs(title="Gross Home Prices in Boulder County") +
  mapTheme()
```

### Internal Characteristics Selected

Variables of interest: 
- 




### Boulder Open Spaces and Roads

```{r Open and Roads, echo=FALSE, message=FALSE, warning=FALSE}

#Grab open space data set
openspace <- 
  st_read("~/CPLNPennDesign/590-Musa/Musa508-Vero/MUSA-508/Midterm/County_Open_Space.geojson") %>%
  filter(!is.na(PARK_GROUP)) %>%
  st_transform('ESRI:102653')


```

### Roads 

```{r}
#Grab road data set
roads.sf <-
  st_read("https://opendata.arcgis.com/datasets/f8292cbf379e4df7b9b8f62e21120ea7_0.geojson") %>%
  st_transform('ESRI:102653') %>% 
  dplyr::select(OBJECTID, STREET_NAME, SPECIFIC_CATEGORY, geometry) %>%
  filter(SPECIFIC_CATEGORY %in% c("State", "Municipal Primary")) %>%


ggplot() +
  geom_sf(data = boulderCounty, fill = "grey90") +
  geom_sf(data = clip, aes(colour = SPECIFIC_CATEGORY)) +
  labs(title="Boulder County Roads") +
  mapTheme()

boulder.sf <-
  boulder.sf %>%
    mutate(
      roads_n = st_nearest_feature(boulder.sf,roads.sf,check_crs = TRUE,longlat =
                                isTRUE(st_is_longlat(boulder.sf))))

#Buffer distance
roadBuffer <- 
  rbind(
    st_buffer(roads.sf, 2640) %>%
      mutate(Legend = "1/2mi Buffer") %>%
      dplyr::select(Legend),
  st_union(st_buffer(roads.sf, 2640)) %>%
      st_sf() %>%
      mutate(Legend = "Unioned Buffer"))

Unioned_buffer <- filter(roadBuffer, Legend=="Unioned Buffer")

boulder.sf <- 
  st_join(boulder.sf, Unioned_buffer,join = st_intersects,
  #suffix = c(".x", ".y"),
  left = TRUE, largest = FALSE)
    
ls1 = roads.sf[]

boulder.sf <- 
  rbind(
    st_centroid(boulder.sf)[buffer,] %>%
      st_drop_geometry() %>%
      left_join(allTracts) %>%
      st_sf() %>%
      mutate(TOD = "TOD"),
    st_centroid(allTracts)[buffer, op = st_disjoint] %>%
      st_drop_geometry() %>%
      left_join(allTracts) %>%
      st_sf() %>%
      mutate(TOD = "Non-TOD"))

ggplot() +
  geom_sf(data = boulderCounty, fill = "grey90") +
  #geom_sf(data = roads.sf, fill = "black") +
  geom_sf(data = Unioned_buffer, fill = NA) +
  geom_sf(data = boulder.sf, aes(colour = q5(roads_n)), 
          show.legend = "point", size = .5) +
  scale_color_manual(values = palette5,
                   labels = qBr(boulder.sf, "roads_n"),
                   name = "Quintile\nBreaks") +
  geom_sf_label(data = muni, aes(label = ZONEDESC), size = 2) +
  labs(title="Distances of Homes to Roads in meters") +
  mapTheme()

```
  




### OSM Data for Boulder County

Grab OSM data for Boulder County
Check out the wiki for the key/value pairs for different amenities - that lets you #figure out what you can call from OSM #https://wiki.openstreetmap.org/wiki/Category:Tag_descriptions_by_value

set bounding box - the maximum x-y extent you are interested in

```{r OSM, echo=FALSE}
install.packages("osmdata")
library(osmdata)
library(tigris)


# Do some right-clicking in google maps to figure this out
q0 <- opq(bbox = c(-75.3,39.85,-74.9,40.15)) #bounding box for philly
q0 <- opq(bbox = c(-105.21,36.00,40.05,24.00)) #bounding box for boulder
q0 <- opq(bbox = c("Boulder County")) #bounding box for boulder


# Parks
park <- add_osm_feature(opq = q0, key = 'leisure', value = "park") %>%
  osmdata_sf(.)

park.sf <- st_geometry(park$osm_polygons) %>%
  st_as_sf(crs = 4326, agr = "constant") %>%
  st_transform('ESRI:102286') %>%
  cbind(., park$osm_polygons$name) %>%
  rename(NAME = park.osm_polygons.name, geometry = "x")

# Park Centroids
parks_sf_cent <- st_centroid(park.sf)

#Counts of parks per buffer of home price
boulder.sf$parks.buffer =
    st_buffer(boulder.sf, 804.672) %>% 
    aggregate(mutate(parks_sf_cent, counter = 1),., sum) %>%
    pull(counter)
#Keeps giving me this error but not sure how to fix it...Error in st_geos_binop("intersects", #  x, y, sparse = sparse, prepared = prepared,  : 
#  st_crs(x) == st_crs(y) is not TRUE


# Transportation - Subway
subway <- add_osm_feature(opq = q0, key = 'railway', value = "subway") %>%
  osmdata_sf(.)
subway.sf <- st_geometry(subway$osm_lines) %>%
  st_transform(4326) %>%
  st_sf() %>%
  cbind(., subway$osm_lines$name) %>%
  rename(NAME = subway.osm_lines.name) %>%
  filter(NAME %in% c("Market-Frankford Line", "Broad Street Line"))

# Amenities - Restaurant
# Check in the attributes of `restaurant` and see what the different
# variables and values are.
# These data seem really shaky by the way
restaurant <- add_osm_feature(opq = q0, key = 'amenity', value = "restaurant") %>%
  osmdata_sf(.)
restaurant.sf <- st_geometry(restaurant$osm_points) %>%
  st_transform(4326) %>%
  st_sf() %>%
  cbind(., restaurant$osm_points$amenity) %>%
  rename(NAME = restaurant.osm_points.amenity)

# Amenities - Hospitals + Clinics
hospitals <- add_osm_feature(opq = q0, key = 'amenity', value = "hospital") %>%
  osmdata_sf(.)
hospitals.sf <- st_geometry(hospitals$osm_points) %>%
  st_transform(4326) %>%
  st_sf() %>%
  cbind(., hospitals$osm_points$amenity) %>%
  rename(NAME = hospitals.osm_points.amenity) %>%
  #mutate(NAME = is.na(NAME),"hospital")

clinics <- add_osm_feature(opq = q0, key = 'amenity', value = "clinic") %>%
  osmdata_sf(.)
clinics.sf <- st_geometry(clinics$osm_points) %>%
  st_transform(4326) %>%
  st_sf() %>%
  cbind(., clinics$osm_points$amenity) %>%
  rename(NAME = clinics.osm_points.amenity)

healthcare <- rbind(hospitals.sf,clinics.sf)


# Amenities - Education (Schools, Colleges, Universities)
schools <- add_osm_feature(opq = q0, key = 'amenity', value = "school") %>%
  osmdata_sf(.)
schools.sf <- st_geometry(schools$osm_points) %>%
  st_transform(4326) %>%
  st_sf() %>%
  cbind(., schools$osm_points$amenity) %>%
  rename(NAME = schools.osm_points.amenity)

uni <- add_osm_feature(opq = q0, key = 'amenity', value = "university") %>%
  osmdata_sf(.)
uni.sf <- st_geometry(uni$osm_points) %>%
  st_transform(4326) %>%
  st_sf() %>%
  cbind(., uni$osm_points$osm_id) %>% 
  rename(NAME = uni.osm_points.osm_id)

education <- rbind(schools.sf,uni.sf) 

# Add the features for Boulder County
# You can use this to clip things if it's necessary
coCounties <- counties(state = 'CO', cb = FALSE)

boulder <- coCounties %>%
  filter(NAME == "Boulder") %>%
  st_as_sf() %>%
  st_transform(4326)


#Visualize it
ggplot() +
  geom_sf(data = boulderCounty, fill = "grey90") +
  geom_sf(data = schools.sf, aes(colour = "#ffcdb2"), show.legend = FALSE, size = .25) +
  labs(title="Parks in Boulder County") +
  mapTheme()


```

## Census Data
```{r message=FALSE, warning=FALSE}
# Load census API key
census_api_key("7fcf0c60997f4d8ccd298e26df0b2f35dc033150",install=TRUE, overwrite=TRUE)

#Load list of variables
acs_variable_list.2019 <- load_variables(2019,"acs5")

#Variables to test from Census:
#pctBachelor: B06009_005
#WorkedFromHome: B99087_005
#Age: B01002_001


```



## Summary Statistics: Physical variables, Amenities, and Spatial Process

```{r}

#Data selection step

#Distance to Parks & Open Spaces

#Distance to Restaurants

#Distance to Roads

#Distance to Subway

#Distance to Educational Institutions

#Distance to Healthcare Facilities

```

## Home Buffer
```{r}

#A 5 mile buffer is created from Boulder homes 
BoHomeBuffers <- 
  rbind(
    st_buffer(boulder.sf, 804.672) %>%
      mutate(Legend = "5mi Buffer") %>%
      dplyr::select(Legend),
  st_union(st_buffer(boulder.sf, 804.672)) %>%
      st_sf() %>%
      mutate(Legend = "Unioned Buffer"))


#Home MRBuffer to measure distance from roads
Unioned_buffer <- filter(BoHomeBuffers, Legend=="Unioned Buffer")
```


## Defining Correlation to continuous variables using nearest nn function 
```{r}
boulder.sf$parks.Buffer =
    st_buffer(boulder.sf, 660) %>% 
    aggregate(mutate(parks_sf_cent, counter = 1),., sum) %>%
    pull(counter)

#Nearest neighbor function
st_c <- st_coordinates

boulder.sf <-
  boulder.sf %>% 
    mutate(
      parks_nn1 = nn_function(st_c(boulder.sf), st_c(parks_sf_cent), 1),
      parks_nn2 = nn_function(st_c(boulder.sf), st_c(parks_sf_cent), 2),
      parks_nn3 = nn_function(st_c(boulder.sf), st_c(parks_sf_cent), 3),
      parks_nn4 = nn_function(st_c(boulder.sf), st_c(parks_sf_cent), 4),
      parks_nn5 = nn_function(st_c(boulder.sf), st_c(parks_sf_cent), 5))


```

```{r  echo=FALSE, message=FALSE, warning=FALSE}
```

## Exploratory Analysis: Correlation Plots

```{r correlation pt 1 echo=FALSE, message=FALSE, warning=FALSE}

#ggplot(filter(boulder.sf, price <= 2000000), aes(y=price, x = GarageSize), show.legend = "point", size = .5) +
#  geom_point(size = .5) +
 # geom_smooth(method = "lm") +
  #labs(title = "Price as a function of Size", y = "Price") +
  #plotTheme()

#Home Characteristics Corr Plots
st_drop_geometry(boulder.sf) %>% 
  mutate(Age = 2015 - builtYear) %>%
  dplyr::select(price, Size, Age, TotalBedrooms, GarageSize, ) %>%
  filter(price <= 1000000, Age < 500) %>%
  gather(Variable, Value, -price) %>% 
  ggplot(aes(Value, price)) +
     geom_point(size = .5) + geom_smooth(method = "lm", se=F, colour = "#FA7800") +
     facet_wrap(~Variable, ncol = 4, scales = "free") +
     labs(title = "Price as a function of continuous variables") +
     plotTheme()
```
```{r correlation pt. 2 echo=FALSE, message=FALSE, warning=FALSE}

st_drop_geometry(boulder.sf) %>% 
  mutate(Age = 2015 - builtYear) %>%
  dplyr::select(price, Age, TotalBathrooms, mainfloorSF, Ac) %>%
  filter(price <= 1000000, Age < 500) %>%
  gather(Variable, Value, -price, -Age) %>% 
  ggplot(aes(Value, price)) +
     geom_point(size = .5) + geom_smooth(method = "lm", se=F, colour = "#FA7800") +
     facet_wrap(~Variable, ncol = 4, scales = "free") +
     labs(title = "Price as a function of continuous variables") +
     plotTheme()
```

### Correlation to Categorical Variables

Price as a function of non numeric variables

```{r}

st_drop_geometry(boulder.sf) %>% 
  dplyr::select(price, designCodeDscr, ConstCodeDscr, IntWallDscr) %>%
  filter(price <= 1000000) %>%
  gather(Variable, Value, -price) %>% 
   ggplot(aes(Value, price)) +
     geom_bar(position = "dodge", stat = "summary", fun.y = "mean", scientific = FALSE) +
     facet_wrap(~Variable, ncol = 3, scales = "free") +
     labs(title = "Price as a function of categorical variables", y = "Mean_Price") +
     plotTheme() + theme(axis.text.x = element_text(angle = 90, hjust = 1))

```
### Regressions for determining correlation strength

Internal characteristics of homes
```{r}
reg1 <- lm(price ~ Size, data = boulder.sf)

#Table 1 Kable-Tidy
lm(price ~ Size, data = boulder.sf) %>%
  tidy() %>%
  mutate(p.value = scales::pvalue(p.value))%>%
  kable(
    caption = "Coefficient-Level Estimates for a Model Fitted to Predict Home Prices in 
    Boulder County", 
    col.names = c("Predictor", "Estimate", "Std.Err", "t-stat", "p-value"), 
    digits = c(0, 2, 3, 2, 3),
    align = c("l", "r", "r", "r", "r")
  ) %>%
  kable_styling()
    
summary(reg1)


#Table 1 (Stargazer)
stargazer(reg1, type = "html", 
          dep.var.labels=c("Price total"),
          covariate.labels=c("Size in sqm"))

```


```{r}
head(boulder.sf)

reg2 <- lm(price ~ ., data = st_drop_geometry(boulder.sf) %>% 
                                 dplyr::select(price, Size, builtYear, GarageSize,
                                               mainfloorSF, TotalBedrooms, 
                                               TotalBathrooms))
summary(reg2)



reg3 <- lm(price ~ ., data = st_drop_geometry(boulder.sf) %>% 
                                 dplyr::select(price, Size, builtYear, 
                                               TotalBedrooms, TotalBathrooms, 
                                               bsmtSF, parks_nn1, parks_nn2))
summary(reg3)

#Coefficients of all models
plot_summs(reg1, reg3, reg2)

```




```{r}
#Parks Correlation

boulder.sf %>%
  st_drop_geometry() %>%
  mutate(Age = 2015 - builtYear) %>%
  dplyr::select(price, starts_with("parks_")) %>%
  filter(price <= 1000000) %>%
  gather(Variable, Value, -price) %>% 
   ggplot(aes(Value, price)) +
     geom_point(size = .5) + geom_smooth(method = "lm", se=F, colour = "#FA7800") +
     facet_wrap(~Variable, nrow = 1, scales = "free") +
     labs(title = "Price as a function of continuous variables: Nearest Parks") +
     plotTheme()


```


## Correlation Matrix

```{r message=FALSE, warning=FALSE, paged.print=FALSE, echo=FALSE}

numericVars <- 
  select_if(st_drop_geometry(boulder.sf), is.numeric) %>% na.omit()


ggcorrplot(
  round(cor(numericVars), 1), 
  p.mat = cor_pmat(numericVars),
  show.diag = TRUE,
  colors = c("#25CB10", "white", "#FA7800"),
  type="lower",
  insig = "blank") +  
    labs(title = "Correlation across numeric variables")

```

## Mean absolute error MAE by Municipality

```{r}

#Grouping prediction data by muni
left_join(
  st_drop_geometry(boston.test) %>%
    group_by(Name) %>%
    summarize(meanPrice = mean(SalePrice, na.rm = T)),
  mutate(boston.test, predict.fe = 
                        predict(lm(SalePrice ~ Name, data = boston.test), 
                        boston.test)) %>%
    st_drop_geometry %>%
    group_by(Name) %>%
      summarize(meanPrediction = mean(predict.fe))) %>%
      kable() %>% kable_styling()


#Prediction Data by Municipality
reg.nhood <- lm(SalePrice ~ ., data = as.data.frame(boston.training) %>% 
                                 dplyr::select(Name, SalePrice, LivingArea, 
                                               Style, GROSS_AREA, NUM_FLOORS.cat,
                                               R_BDRMS, R_FULL_BTH, R_HALF_BTH, 
                                               R_KITCH, R_AC, R_FPLACE,crimes.Buffer))

boston.test.nhood <-
  boston.test %>%
  mutate(Regression = "Neighborhood Effects",
         SalePrice.Predict = predict(reg.nhood, boston.test),
         SalePrice.Error = SalePrice.Predict- SalePrice,
         SalePrice.AbsError = abs(SalePrice.Predict- SalePrice),
         SalePrice.APE = (abs(SalePrice.Predict- SalePrice)) / SalePrice)%>%
  filter(SalePrice < 5000000)


#binds error metrics
bothRegressions <- 
  rbind(
    dplyr::select(boston.test, starts_with("SalePrice"), Regression, Name) %>%
      mutate(lagPriceError = lag.listw(spatialWeights.test, SalePrice.Error)),
    dplyr::select(boston.test.nhood, starts_with("SalePrice"), Regression, Name) %>%
      mutate(lagPriceError = lag.listw(spatialWeights.test, SalePrice.Error))) 

```

## Scatterplot plot of MAPE by neighborhood as a function of mean price

```{r}

st_drop_geometry(bothRegressions) %>%
  group_by(Regression, Name) %>%
  summarize(mean.MAPE = mean(SalePrice.APE, na.rm = T)) %>%
  ungroup() %>% 
  left_join(nhoods) %>%
    st_sf() %>%
    ggplot() + 
      geom_sf(aes(fill = mean.MAPE)) +
      geom_sf(data = bothRegressions, colour = "black", size = .5) +
      facet_wrap(~Regression) +
      scale_fill_gradient(low = palette5[1], high = palette5[5],
                          name = "MAPE") +
      labs(title = "Mean test set MAPE by neighborhood") +
      mapTheme()

#Table differentiating MAPE from MAE
st_drop_geometry(bothRegressions) %>%
  gather(Variable, Value, -Regression, -Name) %>%
  filter(Variable == "SalePrice.AbsError" | Variable == "SalePrice.APE") %>%
  group_by(Regression, Variable) %>%
    summarize(meanValue = mean(Value, na.rm = T)) %>%
    spread(Variable, meanValue) %>%
    kable()


```

