---
title: "Midterm"
author: "Me"
date: "10/8/2021"
output: 
  html_document:
    toc: true
    theme: united
---


## Project Description

This project is...

The following libraries are needed in for this model:

library(tidyverse)
library(tidycensus)
library(sf)
library(spdep)
library(caret)
library(ckanr)
library(FNN)
library(grid)
library(gridExtra)
library(ggcorrplot)
library(kableExtra)
library(jtools) 
library(ggstance) 
library(stargazer)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Libraries needed for this exercise
library(tidyverse)
library(tidycensus)
library(sf)
library(spdep)
library(caret)
library(ckanr)
library(FNN)
library(grid)
library(gridExtra)
library(ggcorrplot)
library(kableExtra)
library(jtools)     # for regression model plots
library(ggstance) 
library(stargazer)

# Functions and data directory
root.dir = "https://raw.githubusercontent.com/veronicaUPenn22/Public-Policy-Analytics-Landing/master/DATA/"

source("https://raw.githubusercontent.com/veronicaUPenn22/Public-Policy-Analytics-Landing/master/functions.r")

# Color palette
palette5 <- c("#ffcdb2","#ffb4a2","#e5989b","#b5838d","#6d6875")

```

### Data Gathering Methods

For this project, we used the dfollowing data sets:

| Dataset        | Description    | Open Data URL  | File Type | Location |
| :------------- | :------------- | :------------- | :------------- | :------------- |
| Boulder County Municipalities | Boundaries polygons | https://opendata-bouldercounty.hub.arcgis.com/datasets/bouldercounty::municipalities/about | geojson | MUSA-508/Midterm |
| Boulder County Boundary | Boundary polygon | https://opendata-bouldercounty.hub.arcgis.com/datasets/county-boundary/explore?location=40.088157%2C-105.373097%2C11.58 | geojson | MUSA-508/Midterm |
| Boulder County Open Spaces | Boundaries for parks and open spaces state and municipally owned | https://opendata-bouldercounty.hub.arcgis.com/datasets/county-open-space/explore?location=40.080100%2C-105.341850%2C11.48&showTable=true | geojson | MUSA-508/Midterm |
| Roads | Boulder County main freeways and road network | https://opendata.arcgis.com/datasets/f8292cbf379e4df7b9b8f62e21120ea7_0.geojson | geojson | "" |



| Student Data | Homes data for Boulder County (2019-2021) | Provided by MUSA508 instructors | geojson | MUSA-508/Midterm |


```{r}

```


### Boulder Data and Homes Data 

```{r cars}

# Load census API key
census_api_key("7fcf0c60997f4d8ccd298e26df0b2f35dc033150",install=TRUE, overwrite=TRUE)

muni <- 
  st_read("~/CPLNPennDesign/590-Musa/Musa508-Vero/MUSA-508/Midterm/Municipalities.geojson") %>%
  st_transform('ESRI:102653')

studentData <- 
  st_read("~/CPLNPennDesign/590-Musa/Musa508-Vero/MUSA-508/Midterm/studentData.geojson", crs = 'ESRI:102254') %>%
  st_transform('ESRI:102653')

boulderCounty <-
  st_read("~/CPLNPennDesign/590-Musa/Musa508-Vero/MUSA-508/Midterm/County_Boundary.geojson")%>%
  st_transform('ESRI:102653')

boulder.sf <- studentData %>%
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326, agr = "constant") %>%
  st_transform('ESRI:102653') %>%
  mutate(TotalBathrooms = nbrThreeQtrBaths + nbrFullBaths + nbrHalfBaths) %>%
  rename(Size = TotalFinishedSF, 
         TotalBedrooms = nbrBedRoom, 
         GarageSize = carStorageSF)
  
boulder.sf <-
  





#State Plane Colorado - ESRI:102653
#Colorado North - ESRI:102253
#Colorado Central - ESRI:102254
#Boulder - SR-ORG:7992  

```

### Internal Characteristics Selected

Variables of interest: 
- 




### Boulder Open Spaces and Roads

```{r Open and Roads, echo=FALSE}

#Grab open space data set
openspace <- 
  st_read("~/CPLNPennDesign/590-Musa/Musa508-Vero/MUSA-508/Midterm/County_Open_Space.geojson") %>%
  filter(!is.na(PARK_GROUP)) %>%
  st_transform('ESRI:102653')

#Grab road data set
roads.sf <-
  st_read("https://opendata.arcgis.com/datasets/f8292cbf379e4df7b9b8f62e21120ea7_0.geojson") %>%
  st_transform('ESRI:102653') %>% 
  dplyr::select(OBJECTID, STREET_NAME, SPECIFIC_CATEGORY, geometry) %>%
  filter(SPECIFIC_CATEGORY %in% c("State", "Municipal Primary"))


ggplot() +
  geom_sf(data = boulderCounty, fill = "grey90") +
  geom_sf(data = roads, aes(colour = SPECIFIC_CATEGORY)) +
  labs(title="Boulder County Roads") +
  mapTheme()

```

### OSM Data for Boulder County

Grab OSM data for Boulder County
Check out the wiki for the key/value pairs for different amenities - that lets you #figure out what you can call from OSM #https://wiki.openstreetmap.org/wiki/Category:Tag_descriptions_by_value

set bounding box - the maximum x-y extent you are interested in

```{r OSM, echo=FALSE}
install.packages("osmdata")
library(osmdata)
library(tigris)


# Do some right-clicking in google maps to figure this out
q0 <- opq(bbox = c(-75.3,39.85,-74.9,40.15)) #bounding box for philly
q0 <- opq(bbox = c(-105.21,36.00,40.05,24.00)) #bounding box for boulder
q0 <- opq(bbox = c("Boulder County")) #bounding box for boulder


# Parks
park <- add_osm_feature(opq = q0, key = 'leisure', value = "park") %>%
  osmdata_sf(.)

park.sf <- st_geometry(park$osm_polygons) %>%
  st_as_sf(crs = 4326, agr = "constant") %>%
  st_transform('ESRI:102286') %>%
  cbind(., park$osm_polygons$name) %>%
  rename(NAME = park.osm_polygons.name, geometry = "x")

# Park Centroids
parks_sf_cent <- st_centroid(park.sf)

#Counts of parks per buffer of home price
boulder.sf$parks.buffer =
    st_buffer(boulder.sf, 804.672) %>% 
    aggregate(mutate(parks_sf_cent, counter = 1),., sum) %>%
    pull(counter)
#Keeps giving me this error but not sure how to fix it...Error in st_geos_binop("intersects", #  x, y, sparse = sparse, prepared = prepared,  : 
#  st_crs(x) == st_crs(y) is not TRUE


# Transportation - Subway
subway <- add_osm_feature(opq = q0, key = 'railway', value = "subway") %>%
  osmdata_sf(.)
subway.sf <- st_geometry(subway$osm_lines) %>%
  st_transform(4326) %>%
  st_sf() %>%
  cbind(., subway$osm_lines$name) %>%
  rename(NAME = subway.osm_lines.name) %>%
  filter(NAME %in% c("Market-Frankford Line", "Broad Street Line"))

# Amenities - Restaurant
# Check in the attributes of `restaurant` and see what the different
# variables and values are.
# These data seem really shaky by the way
restaurant <- add_osm_feature(opq = q0, key = 'amenity', value = "restaurant") %>%
  osmdata_sf(.)
restaurant.sf <- st_geometry(restaurant$osm_points) %>%
  st_transform(4326) %>%
  st_sf() %>%
  cbind(., restaurant$osm_points$amenity) %>%
  rename(NAME = restaurant.osm_points.amenity)

# Amenities - Hospitals + Clinics
hospitals <- add_osm_feature(opq = q0, key = 'amenity', value = "hospital") %>%
  osmdata_sf(.)
hospitals.sf <- st_geometry(hospitals$osm_points) %>%
  st_transform(4326) %>%
  st_sf() %>%
  cbind(., hospitals$osm_points$amenity) %>%
  rename(NAME = hospitals.osm_points.amenity) %>%
  #mutate(NAME = is.na(NAME),"hospital")


clinics <- add_osm_feature(opq = q0, key = 'amenity', value = "clinic") %>%
  osmdata_sf(.)
clinics.sf <- st_geometry(clinics$osm_points) %>%
  st_transform(4326) %>%
  st_sf() %>%
  cbind(., clinics$osm_points$amenity) %>%
  rename(NAME = clinics.osm_points.amenity)

healthcare <- rbind(hospitals.sf,clinics.sf)



# Amenities - Education (Schools, Colleges, Universities)
schools <- add_osm_feature(opq = q0, key = 'amenity', value = "school") %>%
  osmdata_sf(.)
schools.sf <- st_geometry(schools$osm_points) %>%
  st_transform(4326) %>%
  st_sf() %>%
  cbind(., schools$osm_points$amenity) %>%
  rename(NAME = schools.osm_points.amenity)

uni <- add_osm_feature(opq = q0, key = 'amenity', value = "university") %>%
  osmdata_sf(.)
uni.sf <- st_geometry(uni$osm_points) %>%
  st_transform(4326) %>%
  st_sf() %>%
  cbind(., uni$osm_points$amenity, ) %>% #cbind is giving me an error, not sure how to fix it: arguments imply differing number of rows: 400, 0.
  rename(NAME = uni.osm_points.amenity)

education <- rbind(schools.sf,uni.sf) #because uni.sf doesn't have the NAME column the rbind cannot be made as in healthcare

# Add the features for Boulder County
# You can use this to clip things if it's necessary
coCounties <- counties(state = 'CO', cb = FALSE)

boulder <- coCounties %>%
  filter(NAME == "Boulder") %>%
  st_as_sf() %>%
  st_transform(4326)


#Visualize it
ggplot() +
  geom_sf(data = boulderCounty, fill = "grey90") +
  geom_sf(data = schools.sf, aes(colour = "#ffcdb2"), show.legend = FALSE, size = .25) +
  labs(title="Parks in Boulder County") +
  mapTheme()


ggplot() +
  geom_sf(data = boulderCounty, fill = "grey90") +
  geom_sf(data = boulder.sf, aes(colour = q5(price)), 
          show.legend = "point", size = .75) +
  scale_colour_manual(values = palette5,
                   labels=qBr(boulder.sf,"Price"),
                   name="Quintile\nBreaks") +
  labs(title="Gross Price Boulder") +
  mapTheme()

```

## Census Data
```{r message=FALSE, warning=FALSE}
# Load census API key
census_api_key("7fcf0c60997f4d8ccd298e26df0b2f35dc033150",install=TRUE, overwrite=TRUE)

#Load list of variables
acs_variable_list.2019 <- load_variables(2019,"acs5")

#Variables to test from Census:
#pctBachelor: B06009_005
#WorkedFromHome: B99087_005
#Age: B01002_001


```



## Summary Statistics: Physical variables, Amenities, and Spatial Process

```{r}

#Data selection step

#Distance to Parks & Open Spaces

#Distance to Restaurants

#Distance to Roads

#Distance to Subway

#Distance to Educational Institutions

#Distance to Healthcare Facilities

```

## Home Buffer
```{r}

#A 5 mile buffer is created from Boulder homes 
BoHomeBuffers <- 
  rbind(
    st_buffer(boulder.sf, 804.672) %>%
      mutate(Legend = "5mi Buffer") %>%
      dplyr::select(Legend),
  st_union(st_buffer(boulder.sf, 804.672)) %>%
      st_sf() %>%
      mutate(Legend = "Unioned Buffer"))


#Home MRBuffer to measure distance from roads
Unioned_buffer <- filter(BoHomeBuffers, Legend=="Unioned Buffer")
```


## Defining Correlation to continuous variables using nearest nn function 
```{r}
boulder.sf$parks.Buffer =
    st_buffer(boulder.sf, 660) %>% 
    aggregate(mutate(parks_sf_cent, counter = 1),., sum) %>%
    pull(counter)

#Nearest neighbor function
st_c <- st_coordinates


boulder.sf <-
  boulder.sf %>% 
    mutate(
      parks_nn1 = nn_function(st_c(boulder.sf), st_c(parks_sf_cent), 1),
      parks_nn2 = nn_function(st_c(boulder.sf), st_c(parks_sf_cent), 2),
      parks_nn3 = nn_function(st_c(boulder.sf), st_c(parks_sf_cent), 3),
      parks_nn4 = nn_function(st_c(boulder.sf), st_c(parks_sf_cent), 4),
      parks_nn5 = nn_function(st_c(boulder.sf), st_c(parks_sf_cent), 5))


ggplot() +
  geom_sf(data = boulderCounty, fill = "grey90") +
  geom_sf(data=Unioned_buffer, fill = NA) +
  geom_sf(data = boulder.sf, aes(colour = q5(price)), 
          show.legend = "point", size = .75) +
  scale_colour_manual(values = palette5,
                   labels=qBr(boulder.sf,"Price"),
                   name="Quintile\nBreaks") +
  labs(title="Home Price Buffer: 5 mile. Boulder County") +
  mapTheme()

```

## Exploratory Analysis: Correlation Plots

```{r}

#Home Characteristics Corr
st_drop_geometry(boulder.sf) %>% 
  mutate(Age = 2015 - builtYear) %>%
  dplyr::select(price, Size, Age, TotalBedrooms) %>%
  filter(price <= 1000000, Age < 500) %>%
  gather(Variable, Value, -price) %>% 
   ggplot(aes(Value, price)) +
     geom_point(size = .5) + geom_smooth(method = "lm", se=F, colour = "#FA7800") +
     facet_wrap(~Variable, ncol = 3, scales = "free") +
     labs(title = "Price as a function of continuous variables") +
     plotTheme()
```
```{r}
#Parks Correlation

boulder.sf %>%
  st_drop_geometry() %>%
  mutate(Age = 2015 - builtYear) %>%
  dplyr::select(price, starts_with("parks_")) %>%
  filter(price <= 1000000) %>%
  gather(Variable, Value, -price) %>% 
   ggplot(aes(Value, price)) +
     geom_point(size = .5) + geom_smooth(method = "lm", se=F, colour = "#FA7800") +
     facet_wrap(~Variable, nrow = 1, scales = "free") +
     labs(title = "Price as a function of continuous variables: Nearest Parks") +
     plotTheme()


```


## Correlation Matrix

```{r message=FALSE, warning=FALSE, paged.print=FALSE, echo=FALSE}

numericVars <- 
  select_if(st_drop_geometry(boulder.sf), is.numeric) %>% na.omit()


ggcorrplot(
  round(cor(numericVars), 1), 
  p.mat = cor_pmat(numericVars),
  show.diag = TRUE,
  colors = c("#25CB10", "white", "#FA7800"),
  type="lower",
  insig = "blank") +  
    labs(title = "Correlation across numeric variables")

```



