---
title: "Midterm"
author: "Me"
date: "10/8/2021"
output: 
  html_document: 
    toc: yes
    theme: united
    code_folding: hide
editor_options: 
  chunk_output_type: inline
---

# Introduction

This project aims to develop a model that can predict future home values by using geospatial machine learning processes. We basically deconstruct the different components and constituents that could describe a home and its value. As we know, usually market rate and economic valuation under capitalist systems are based on subjective factors that can be geographically identified. In a national scale, a home's location for example, might influence it's valuation over many other variables. In a more local scale, we could have both cases. First is the clustering of similar price ranges based on similarity across. Second is a differentiated price based on unique qualities of a home in contrast with its closest homes, which is often described with non-numerical factors such as aesthetic value, historical significance, style, materials, etc. 

In this model we mainly focus on the first, but we do not fully dismiss non-numerical characteristics that could help predict future home prices as well. 


# Modeling strategy and Methodology:

To develop the model we gathered all the data from Boulder Open Data, Open Street Map and the U.S. Census. We used geojson and API file formats. Secondly, we turned the homes data (provided by the instructors) into an spatial feature dataset that was then joined to the multiple external variables (parks, education, health, roads, hazards, income and age groups to name a few). Following this we did an exploratory analysis of the dataset and visualized the correlation of home prices to both internal and external variables using an ordinary least square (OLS) matrix. We used multivariate regressions to test model's fitness and which variable groups are stronger predictors than other after seeing OLS relationships. Afterwards we splitted the data into a training set (0) and a test set (1), that is then used to predict home sale prices for the Boulder County homes. This is evaluated for generalizability in the end, meaning that a second training/test model is done at the municipality scale to check if the model is a good predictor for different contexts across groups and not just our selected geography. 

# Summary of results:




## Getting Started

The libraries, directory and functions in the below code block are needed for this model:


```{r setup, include=FALSE}
knitr::opts_chunk$set(include = FALSE)

#Libraries needed for this exercise
library(tidyverse)
library(tidycensus)
library(sf)
library(spdep)
library(caret)
library(ckanr)
library(FNN)
library(grid)
library(gridExtra)
library(ggcorrplot)
library(kableExtra)
library(jtools)     # for regression model plots
library(ggstance) 
library(stargazer)

# Functions and data directory
root.dir = "https://raw.githubusercontent.com/veronicaUPenn22/Public-Policy-Analytics-Landing/master/DATA/"

source("https://raw.githubusercontent.com/veronicaUPenn22/Public-Policy-Analytics-Landing/master/functions.r")

# Color palette
palette5 <- c("#ffcdb2","#ffb4a2","#e5989b","#b5838d","#6d6875")

palette6 <- c("#16537e","#114163","#12234d","#20124d","#351c75")

```


### Data Gathering Methods

Table of data sets

| Dataset        | Description    | Open Data URL  | File Type | Location |
| :------------- | :------------- | :------------- | :------------- | :------------- |
| Boulder County Municipalities | Boundaries polygons | https://opendata-bouldercounty.hub.arcgis.com/datasets/bouldercounty::municipalities/about | geojson | MUSA-508/Midterm |
| Boulder County Boundary | Boundary polygon | https://opendata-bouldercounty.hub.arcgis.com/datasets/county-boundary/explore?location=40.088157%2C-105.373097%2C11.58 | geojson | MUSA-508/Midterm |
| Parks | Boundaries for parks and open spaces state and municipally owned | https://opendata-bouldercounty.hub.arcgis.com/datasets/county-open-space/explore?location=40.080100%2C-105.341850%2C11.48&showTable=true | geojson | MUSA-508/Midterm |
| Student Data | Homes data for Boulder County (2019-2021) | Provided by MUSA508 instructors | geojson | MUSA-508/Midterm |
| Libraries | Points of libraries in Boulder County  | https://opendata.arcgis.com/datasets/7f4ea25ba87345e380d2e896611d2588_0.geojson | geojson | Boulder County Open Data | 
| Restaurants | 5 year ACS 2019 | osmdata package | geojson | OSM |
| Marijuana Establishments | Point data for establishments locations | https://www.bouldercounty.org/government/open-data/ | geojson | MUSA-508/Midterm |
| Schools | Point data of elementary, middle and high schools | https://www.bouldercounty.org/government/open-data/ | geojson | MUSA-508/Midterm |
| Universities | 5 year ACS 2019 | osmdata package | geojson | OSM |
| Healthcare | Clinics and hospitals point data | osmdata package | geojson | OSM |
| Trails | Trails from Open Spaces & Parks | https://www.bouldercounty.org/government/open-data/ | geojson | MUSA-508/Midterm |
| Flood zones |  Inundated high water maker for the Boulder County flood  | https://www.bouldercounty.org/government/open-data/ | geojson | MUSA-508/Midterm |
| Scenic corridors | Boulder County Peak to Peak Corridor | https://www.bouldercounty.org/government/open-data/ | geojson | MUSA-508/Midterm |

### Internal Characteristics: Homes and Boulder Data 

```{r Housing and Boulder shp, echo=TRUE, message=FALSE, warning=FALSE}

muni <- 
  st_read("~/CPLNPennDesign/590-Musa/Musa508-Vero/MUSA-508/Midterm/Municipalities.geojson") %>%
  st_transform('ESRI:102653')

housingData <- 
  st_read("~/CPLNPennDesign/590-Musa/Musa508-Vero/MUSA-508/Midterm/studentData.geojson", crs = 'ESRI:102254') %>%
  st_transform('ESRI:102653')

boulderCounty <-
  st_read("~/CPLNPennDesign/590-Musa/Musa508-Vero/MUSA-508/Midterm/County_Boundary.geojson")%>%
  st_transform('ESRI:102653')

boulder.sf <- housingData %>%
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326, agr = "constant") %>%
  st_transform('ESRI:102653') %>%
  mutate(pricesqft = ifelse(TotalFinishedSF > 0, (price/TotalFinishedSF), 0),
    TotalBathrooms = nbrThreeQtrBaths + nbrFullBaths + nbrHalfBaths) %>%
  rename(Size = TotalFinishedSF, 
         TotalBedrooms = nbrBedRoom, 
         GarageSize = carStorageSF,
         BuildingType = designCodeDscr,
         Quality = qualityCodeDscr,
         YearBuilt = EffectiveYear,
         Construction = ConstCodeDscr,
         Internal = IntWallDscr)


#State Plane Colorado - ESRI:102653
#Colorado North - ESRI:102253
#Colorado Central - ESRI:102254
#Boulder - SR-ORG:7992  

```

## What internal and external factors influence home value?

We selected a few variables that we believe would be good price predictors for home prices in Boulder County. 

Context for external: 
Based on the demographics, it is a relatively white county, with over 85% of the population being white. median income rates are also high in about 80k for median income, doubling the national average. This should explain why ownership is higher than rented homes for example. Most people seem to drive to work, and the average commute in the county is 23 minutes. 
Parks and open spaces are an important highlight of Boulder County as well. These amenities are an attraction to both locals and tourists, probably becoming a strong factor influencing home values relative to their proximity. Physical activity and access to green trails seems important for households in Boulder County. A survey by the Centers for Disease Control found that Colorado had fewer overweight people per capita and more people who exercise than any other state. While most people commute by car to jobs and amenities, it seems that physical activity is described through these natural assets. In a post COVID/work from home scenario, access to these sites might be a strong variable for home price. 
Based on census and fast facts, education, health and leisure seem a priority for Boulder County citizens. Distance to amenities such as schools, colleges, universities, and restaurants are also considered in this project. 

Homes' internal characteristics:
Physical characteristics of the homes are important factors for predicting home values. As in appraisals, the quality, age, size, number of bedrooms and bathrooms all influence it valuation. Functioning characteristics such as AC/Heating and plumbing systems also influence price.


## Gathering External Characteristics

### Census Data

Retrieved from US Census Bureau. ACS 2019 5 year

```{r Census Data, echo=TRUE, message=FALSE, warning=FALSE}
# Load census API key
census_api_key("7fcf0c60997f4d8ccd298e26df0b2f35dc033150",install=TRUE, overwrite=TRUE)

#Load list of variables
acs_variable_list.2019 <- load_variables(2019,"acs5")


#Year 2019 tracts
tracts19 <-  
  get_acs(geography = "tract", variables = c("B25026_001E","B19013_001E","B01002_001E","B02001_002"),
          year=2019, state=08, county=013, geometry=T) %>% 
  st_transform('ESRI:102653')

tracts19 <- 
  tracts19 %>%
  select( -NAME, -moe) %>%
  spread(variable, estimate) %>%
  select(-geometry) %>%
  rename(TotalPop = B25026_001, 
         MedHHInc = B19013_001, 
         medianage = B01002_001,
         WhitePop = B02001_002) 

tracts19 <- 
  tracts19 %>%
  mutate(pctWhite = ifelse(TotalPop > 0, WhitePop / TotalPop, 0))

#point to polygon spatial join
boulder.sf <-
  boulder.sf  %>% 
    mutate(
      st_join(boulder.sf, tracts19, join = st_within))

table(boulder.sf$Internal)

```

### Amenities + Public Services + Hazards


#### Feature Engineering 

Given that some of the variables contain a great amount of outliers we recategorized some of them. This is meant to potentially improve our model's generalizability and prediction power. Less than 40 homes had from 7 to 24 bedrooms, while over 4k houses had 3, we summarized all houses of 7 to 24 bedrooms into one single category (7+). For bathrooms, a similar categorization had to be done, any house with 7 to 12 bathrooms became a single category. 

Na      Brick Concrete    Frame  Masonry  Precast   Veneer     Wood 
75      125        6     9625     1526        2        1        4 

In terms of categorical variables, we recategorized both construction materials and the interiority types into more general categories. Anything classified as masonry, precast, brick and concrete are became "stone based", while veneer, wood, frame, and the unidentified would become "No stone based".

Na        Drywall   Hardwood Panel      Plaster   Plywood     Unfinished    Wall Board 
79        10411     185                 482       32          40            135

In the interiority, we decided to keep drywall, wall board and plaster as separate categoriws, then turn anything wood related into one, and finally putting unfinished and unidentified observations in 5th category.

While these changes may not have made our model stronger, it certainly improved the predictions significantly, originally we only 208 observations in our test data, then we got _____. 


```{r Amenities + Public Services + Hazards, echo=FALSE, message=FALSE, warning=FALSE}
install.packages("osmdata")
library(osmdata)
library(tigris)

q0 <- opq(bbox = c("Boulder County")) #bounding box for boulder

#---- Libraries -----

libraries <-
   st_read("https://opendata.arcgis.com/datasets/7f4ea25ba87345e380d2e896611d2588_0.geojson") %>%
  st_transform(st_crs('ESRI:102653'))

#---- Trails -----

trails <- 
   st_read("https://opendata.arcgis.com/datasets/3a950053bbef46c6a3c2abe3aceee3de_0.geojson") %>%
  st_transform(st_crs('ESRI:102653')) 

#---- Marihuana Establishments -----

marijuanaestablishments <- 
   st_read("https://opendata.arcgis.com/datasets/425a0adb547a4faba4b741a4fe4373b1_0.geojson") %>%
  st_transform(st_crs('ESRI:102653'))


# ----- Schools + Universities----

schools <- 
  st_read("~/CPLNPennDesign/590-Musa/Musa508-Vero/MUSA-508/Midterm/Schools_Boulder.shp") %>%
  st_transform('ESRI:102653')

university <- add_osm_feature(opq = q0, key = 'amenity', value = "university") %>%
  osmdata_sf(.)
university.sf <- st_geometry(university$osm_points) %>%
  st_transform(4326) %>%
  st_sf() %>%
  cbind(., university$osm_points$osm_id) %>% 
  rename(NAME = university.osm_points.osm_id)

#---- Parks ----

parks <- 
  st_read("~/CPLNPennDesign/590-Musa/Musa508-Vero/MUSA-508/Midterm/County_Open_Space.geojson") %>%
  filter(!is.na(PARK_GROUP)) %>%
  st_transform('ESRI:102653')


# ----- Hospitals + Clinics ----
hospitals <- add_osm_feature(opq = q0, key = 'amenity', value = "hospital") %>%
  osmdata_sf(.)
hospitals.sf <- st_geometry(hospitals$osm_points) %>%
  st_transform(4326) %>%
  st_sf() %>%
  cbind(., hospitals$osm_points$amenity) %>%
  rename(NAME = hospitals.osm_points.amenity)

clinics <- add_osm_feature(opq = q0, key = 'amenity', value = "clinic") %>%
  osmdata_sf(.)
clinics.sf <- st_geometry(clinics$osm_points) %>%
  st_transform(4326) %>%
  st_sf() %>%
  cbind(., clinics$osm_points$amenity) %>%
  rename(NAME = clinics.osm_points.amenity)

healthcare <- rbind(hospitals.sf,clinics.sf)


#---- Restaurants -----
restaurant <- add_osm_feature(opq = q0, key = 'amenity', value = "restaurant") %>%
  osmdata_sf(.)
restaurant.sf <- st_geometry(restaurant$osm_points) %>%
  st_transform(4326) %>%
  st_sf() %>%
  cbind(., restaurant$osm_points$amenity) %>%
  rename(NAME = restaurant.osm_points.amenity)


#---- Disaster Risks -----
sceniccorridor <- 
   st_read("https://opendata.arcgis.com/datasets/749ed0a11e454f64a0e5f7c51a786129_0.geojson") %>%
   st_transform(st_crs('ESRI:102653'))

floodzones <-
   st_read("https://opendata.arcgis.com/datasets/a9624bd25d854ef7ab0d543e9490ce48_0.geojson") %>%
   st_transform(st_crs('ESRI:102653'))


#---- Adding features to the home data ----

st_c <- st_coordinates

#libraries
boulder.sf <-
  boulder.sf  %>% 
    mutate(
      libraries_nn1 = nn_function(st_c(boulder.sf), st_c(libraries), 1),
      libraries_nn2 = nn_function(st_c(boulder.sf), st_c(libraries), 2), 
      libraries_nn3 = nn_function(st_c(boulder.sf), st_c(libraries), 3), 
      libraries_nn4 = nn_function(st_c(boulder.sf), st_c(libraries), 4), 
      libraries_nn5 = nn_function(st_c(boulder.sf), st_c(libraries), 5)) 

#trails
boulder.sf <-
  boulder.sf  %>% 
    mutate(
      trails_nn1 = nn_function(st_c(boulder.sf), st_c(trails), 1),
      trails_nn2 = nn_function(st_c(boulder.sf), st_c(trails), 2), 
      trails_nn3 = nn_function(st_c(boulder.sf), st_c(trails), 3), 
      trails_nn4 = nn_function(st_c(boulder.sf), st_c(trails), 4), 
      trails_nn5 = nn_function(st_c(boulder.sf), st_c(trails), 5)) 

#marijuana establishments
boulder.sf <-
  boulder.sf  %>% 
    mutate(
      marijuanaestablishments_nn1 = nn_function(st_c(boulder.sf), st_c(marijuanaestablishments), 1),
      marijuanaestablishments_nn2 = nn_function(st_c(boulder.sf), st_c(marijuanaestablishments), 2), 
      marijuanaestablishments_nn3 = nn_function(st_c(boulder.sf), st_c(marijuanaestablishments), 3), 
      marijuanaestablishments_nn4 = nn_function(st_c(boulder.sf), st_c(marijuanaestablishments), 4), 
      marijuanaestablishments_nn5 = nn_function(st_c(boulder.sf), st_c(marijuanaestablishments), 5))

#schools (elementary school, middle school, high school)
boulder.sf <-
  boulder.sf  %>% 
    mutate(
      schools_nn1 = nn_function(st_c(boulder.sf), st_c(schools), 1),
      schools_nn2 = nn_function(st_c(boulder.sf), st_c(schools), 2), 
      schools_nn3 = nn_function(st_c(boulder.sf), st_c(schools), 3), 
      schools_nn4 = nn_function(st_c(boulder.sf), st_c(schools), 4), 
      schools_nn5 = nn_function(st_c(boulder.sf), st_c(schools), 5)) 

#university
boulder.sf <-
  boulder.sf  %>% 
    mutate(
      university_nn1 = nn_function(st_c(boulder.sf), st_c(university.sf), 1),
      university_nn2 = nn_function(st_c(boulder.sf), st_c(university.sf), 2), 
      university_nn3 = nn_function(st_c(boulder.sf), st_c(university.sf), 3), 
      university_nn4 = nn_function(st_c(boulder.sf), st_c(university.sf), 4), 
      university_nn5 = nn_function(st_c(boulder.sf), st_c(university.sf), 5)) 

# Parks
parks.sf <- st_centroid(parks)

boulder.sf <-
  boulder.sf  %>% 
    mutate(
      parks_nn1 = nn_function(st_c(boulder.sf), st_c(parks.sf),1),
      parks_nn2 = nn_function(st_c(boulder.sf), st_c(parks.sf), 2), 
      parks_nn3 = nn_function(st_c(boulder.sf), st_c(parks.sf), 3), 
      parks_nn4 = nn_function(st_c(boulder.sf), st_c(parks.sf), 4), 
      parks_nn5 = nn_function(st_c(boulder.sf), st_c(parks.sf), 5)) 

#healthcare facilities
boulder.sf <-
  boulder.sf  %>% 
    mutate(
      healthcare_nn1 = nn_function(st_c(boulder.sf), st_c(healthcare), 1),
      healthcare_nn2 = nn_function(st_c(boulder.sf), st_c(healthcare), 2), 
      healthcare_nn3 = nn_function(st_c(boulder.sf), st_c(healthcare), 3), 
      healthcare_nn4 = nn_function(st_c(boulder.sf), st_c(healthcare), 4), 
      healthcare_nn5 = nn_function(st_c(boulder.sf), st_c(healthcare), 5)) 

#restaurants
boulder.sf <-
  boulder.sf  %>% 
    mutate(
      restaurant_nn1 = nn_function(st_c(boulder.sf), st_c(restaurant.sf), 1),
      restaurant_nn2 = nn_function(st_c(boulder.sf), st_c(restaurant.sf), 2), 
      restaurant_nn3 = nn_function(st_c(boulder.sf), st_c(restaurant.sf), 3), 
      restaurant_nn4 = nn_function(st_c(boulder.sf), st_c(restaurant.sf), 4), 
      restaurant_nn5 = nn_function(st_c(boulder.sf), st_c(restaurant.sf), 5)) 

#floodzones
floodzones <-
  floodzones %>%
  mutate(floodzone = 1) %>%
  select(OBJECTID, StreamName, geometry, floodzone)

boulder.sf <-
  st_join(boulder.sf, floodzones, join = st_contains)

boulder.sf$floodzones_1 =
  ifelse(is.na(boulder.sf$floodzone_1),0, 1)


#scenic corridor
sceniccorridor <-
  sceniccorridor %>%
  mutate(sceniccorridor = 1) %>%
  select(OBJECTID, geometry, sceniccorridor)


boulder.sf <-
  st_join(boulder.sf, sceniccorridor) 
boulder.sf$sceniccorridor =
  ifelse(is.na(boulder.sf$sceniccorridor),0, 1)


```

## Home prices spatially distributed across Boulder County.

```{r Price Map, echo=FALSE, message=FALSE, warning=FALSE}

ggplot() +
  geom_sf(data = boulderCounty, fill = "grey90") +
  geom_sf(data = tracts19, fill = NA) +
  geom_sf(data = boulder.sf, aes(colour = q5(price)), 
          show.legend = "point", size = .5) +
  scale_color_manual(values = palette5,
                   labels = qBr(boulder.sf, "price"),
                   name = "Quintile\nBreaks") +
  geom_sf_label(data = muni, aes(label = ZONEDESC), size = 2) +
  labs(title="Gross Home Prices in Boulder County") +
  mapTheme()
```

## Visualizing Independent Variables Spatially

```{r Home Buffer}

#Map of external characteristics // or summary table, however works best
## Home Buffer

#A 5 mile buffer is created from Boulder homes. Graphical purposes only
BoHomeBuffers <- 
  rbind(
    st_buffer(boulder.sf, 2640) %>%
      mutate(Legend = "5mi Buffer") %>%
      dplyr::select(Legend),
  st_union(st_buffer(boulder.sf, 2640)) %>%
      st_sf() %>%
      mutate(Legend = "Unioned Buffer"))

Unioned_buffer <- filter(BoHomeBuffers, Legend=="Unioned Buffer")

```

Libraries, Trails, Marijuana Establishments, Schools, Universities, Parks...

```{r Libraries, echo=TRUE, message=FALSE, warning=FALSE}

LibBuffers <- 
  st_union(st_buffer(libraries, 5280)) %>%
      st_sf() %>%
      mutate(Legend = "Unioned Buffer")

ggplot() +
  geom_sf(data = tracts19, fill = "grey90") +
  geom_sf(data = boulder.sf, aes(colour = q5(price)), show.legend = "point", size = .5) +
  geom_sf(data = LibBuffers, color = "darkred", fill = "transparent") +
  geom_sf(data = libraries, color = "darkred", alpha = .5, size = 3) +
  scale_color_manual(values = palette5,
                   labels = qBr(boulder.sf, "price"),
                   name = "Quintile\nBreaks") +
  labs(title="Distance to Libraries in Boulder County",
       subtitle="0.25mi buffer of distance from amenities"
       ) +
  mapTheme()

```

```{r Trails Distance, echo=FALSE, message=FALSE, warning=FALSE}

TrailsBuffers <- 
  st_union(st_buffer(trails, 5280)) %>%
      st_sf() %>%
      mutate(Legend = "Unioned Buffer")

ggplot() +
  geom_sf(data = tracts19, fill = "grey90") +
  geom_sf(data = boulder.sf, aes(colour = q5(trails_nn1)), show.legend = "point", size = .5) +
  geom_sf(data = TrailsBuffers,color = "darkred", fill = "transparent", size = 0.2) +
  geom_sf(data = trails, color = "darkred", size = 0.5) +
  scale_color_manual(values = palette5,
                   labels = qBr(boulder.sf, "trails_nn1"),
                   name = "Quintile\nBreaks") +
  labs(title="Distance to trails in Boulder County (ft)",
       subtitle="0.25mi buffer of distance from a trail"
       ) +
  mapTheme()

```

```{r Marijuana Establishments, echo=FALSE, message=FALSE, warning=FALSE}


MariBuffers <- 
  st_union(st_buffer(marijuanaestablishments, 5280)) %>%
      st_sf() %>%
      mutate(Legend = "Unioned Buffer")

MariBuffers <- filter(MariBuffers, Legend=="Unioned Buffer")

ggplot() +
  geom_sf(data = tracts19, fill = "grey90") +
  geom_sf(data = boulder.sf, aes(colour = q5(marijuanaestablishments_nn1)), show.legend = "point", size = .5) +
  geom_sf(data = MariBuffers, color = "darkred", fill = "transparent") +
  geom_sf(data = marijuanaestablishments, color = "darkred", alpha = .3, size = 3) +
  scale_color_manual(values = palette5,
                   labels = qBr(boulder.sf, "marijuanaestablishments_nn1"),
                   name = "Quintile\nBreaks") +
  labs(title="Distance to Marijuana Establishments (ft)",
       subtitle="0.25mi buffer of distance from amenities"
       ) +
  mapTheme()

```

```{r Schools, echo=FALSE, message=FALSE, warning=FALSE}

SchoolsBuffers <- 
  st_union(st_buffer(schools, 5280)) %>%
      st_sf() %>%
      mutate(Legend = "Unioned Buffer")

ggplot() +
  geom_sf(data = tracts19, fill = "grey90") +
  geom_sf(data = SchoolsBuffers, color = "darkred", fill = "transparent") +
  geom_sf(data = boulder.sf, aes(colour = q5(schools_nn1)), show.legend = "point", size = .5) +
  geom_sf(data = schools, color = "darkred", alpha = .3, size = 2) +
  scale_color_manual(values = palette5,
                   labels = qBr(boulder.sf, "schools_nn1"),
                   name = "Quintile\nBreaks") +
  labs(title="Distance to Schools (ft)",
       subtitle="0.25mi buffer of distance from amenities"
       ) +
  mapTheme()

```

```{r Universities, echo=FALSE, message=FALSE, warning=FALSE}

UniBuffers <- 
  st_union(st_buffer(university.sf, 1320)) %>%
      st_sf() %>%
      mutate(Legend = "Unioned Buffer")

ggplot() +
  geom_sf(data = tracts19, fill = "grey90") +
  geom_sf(data = boulder.sf, aes(colour = q5(university_nn1)), show.legend = "point", size = .5) +
  geom_sf(data = UniBuffers, color = "darkred", fill = "transparent") +
  geom_sf(data = university.sf, color = "darkred", alpha = .2, size = 3) +
  scale_color_manual(values = palette5,
                   labels = qBr(boulder.sf, "university_nn1"),
                   name = "Quintile\nBreaks") +
  labs(title="Distance to University (ft)",
       subtitle="0.5mi buffer of distance from amenities"
       ) +
  mapTheme()
```

```{r Parks, echo=FALSE, message=FALSE, warning=FALSE}

ggplot() +
  geom_sf(data = tracts19, fill = "grey90") +
  geom_sf(data = parks, color = NA, fill = "#114163", alpha = .6) +
  geom_sf(data = boulder.sf, aes(colour = q5(parks_nn1)), show.legend = "point", size = .5) +
  scale_color_manual(values = palette5,
                   labels = qBr(boulder.sf, "parks_nn1"),
                   name = "Quintile\nBreaks") +
  labs(title="Distance to Parks (ft)",
       subtitle="0.25mi buffer of distance from amenities"
       ) +
  mapTheme()

```

```{r Healthcare Facilities, echo=FALSE, message=FALSE, warning=FALSE}

HealthBuffers <- 
  rbind(
    st_buffer(healthcare, 1320) %>%
      mutate(Legend = "5mi Buffer") %>%
      dplyr::select(Legend),
  st_union(st_buffer(healthcare, 1320)) %>%
      st_sf() %>%
      mutate(Legend = "Unioned Buffer"))

HealthBuffers <- filter(HealthBuffers, Legend=="Unioned Buffer")



ggplot() +
  geom_sf(data = tracts19, fill = "grey90") +
  geom_sf(data = boulder.sf, aes(colour = q5(healthcare_nn1)), show.legend = "point", size = .5) +
  geom_sf(data = healthcare, color = "darkred", alpha = .2, size = 3) +
  geom_sf(data = HealthBuffers,color = "darkred", fill = "transparent") +
  scale_color_manual(values = palette5,
                   labels = qBr(boulder.sf, "healthcare_nn1"),
                   name = "Quintile\nBreaks") +
  labs(title="Distance to Healthcare Facilities (ft)",
       subtitle="0.25mi buffer of distance from amenities"
       ) +
  mapTheme()

```

```{r Restaurants, echo=FALSE, message=FALSE, warning=FALSE}

RestBuffers <- 
  rbind(
    st_buffer(restaurant.sf, 1320) %>%
      mutate(Legend = "5mi Buffer") %>%
      dplyr::select(Legend),
  st_union(st_buffer(restaurant.sf, 1320)) %>%
      st_sf() %>%
      mutate(Legend = "Unioned Buffer"))

RestBuffers <- filter(RestBuffers, Legend=="Unioned Buffer")

ggplot() +
  geom_sf(data = tracts19, fill = "grey90") +
  geom_sf(data = RestBuffers, color = "darkred", fill = "transparent") +
  geom_sf(data = boulder.sf, aes(colour = q5(restaurant_nn3)), show.legend = "point", size = .5) +
  geom_sf(data = restaurant.sf, color = "darkred", alpha = .2, size = 2) +
  scale_color_manual(values = palette5,
                   labels = qBr(boulder.sf, "restaurant_nn3"),
                   name = "Quintile\nBreaks") +
  labs(title="Distance to Restaurants (ft)",
       subtitle="0.25mi buffer of distance from amenities"
       ) +
  mapTheme()

```

```{r Floodzones, echo=FALSE, message=FALSE, warning=FALSE}

FloodBuffers <- 
  st_union(st_buffer(floodzones, 1320)) %>%
      st_sf() %>%
      mutate(Legend = "Unioned Buffer")

ggplot() +
  geom_sf(data = tracts19, fill = "grey90") +
  geom_sf(data = floodzones, color = NA, fill = "#114163", alpha = .6) +
  #geom_sf(data = FloodBuffers, color = "#16537e", fill = "transparent") +
  geom_sf(data = boulder.sf, aes(colour = factor(floodzones_1)), show.legend = "point", size = .8) +
  scale_color_manual(values = c("#e5989b","#351c75")) +
  labs(title="Flood Impacted Homes in Boulder County",
       subtitle="Light grey line is a 0.5mi buffer to have sense of scale of distance from amenities",
       color = "0 is Not affected") +
  mapTheme()

```

```{r Scenic Corridor, echo=FALSE, message=FALSE, warning=FALSE}


ggplot() +
  geom_sf(data = tracts19, fill = "grey90") +
  #geom_sf(data = Unioned_buffer, color = "grey", fill = "transparent") +
  geom_sf(data = sceniccorridor, color = NA, fill = "#114163", alpha = .6) +
  geom_sf(data = boulder.sf, aes(colour = factor(sceniccorridor)), show.legend = "point", size = .5) +
  scale_color_manual(values = c("#e5989b","#351c75")) +
  labs(title="Homes vs Scenic Corridor",
       subtitle="Houses within the scenic corridor",
       color = "0 is Far") +
  mapTheme()

```

```{r Med HH Income, echo=FALSE, message=FALSE, warning=FALSE}


ggplot(tracts19) +
  geom_sf(colour= NA, aes(fill = q5(MedHHInc)), showlegend = TRUE, size = 0.5) +
  #geom_sf(data = Unioned_buffer, color = "grey", fill = "transparent") +
  scale_fill_manual(values = palette6,
                   labels = qBr(tracts19, "MedHHInc"),
                   name = "MedHHIncome") +
  geom_sf(data = boulder.sf, aes(colour = q5(price)), showlegend = "point", size = 0.5) +
  scale_color_manual(values = palette5,
                   labels = qBr(boulder.sf, "price"),
                   name = "Price\nQuintile Breaks")
  labs(title="Med HH Income and Home Prices",
       #subtitle="Light grey line is a 0.5mi buffer to have sense of scale of distance from amenities"
       ) +
  mapTheme()

```

```{r Percent White, echo=FALSE, message=FALSE, warning=FALSE}


ggplot() +
  geom_sf(data = tracts19, colour= NA, aes(fill = q5(pctWhite)), showlegend = TRUE) +
  scale_fill_manual(values = palette6,
                   labels = as.integer(tracts19$pctWhite*100),
                   name = "Percent White") +
  geom_sf(data = boulder.sf, aes(colour = q5(price)), show.legend = "point", size = .5) +
  scale_color_manual(values = palette5,
                   labels = qBr(boulder.sf, "price"),
                   name = "Price\nQuintile Breaks") +
  labs(title="Pct White and Home Prices",
       #subtitle="Light grey line is a 0.5mi buffer to have sense of scale of distance from amenities"
       ) +
  mapTheme()

```

```{r Median Age, echo=FALSE, message=FALSE, warning=FALSE}

ggplot() +
  geom_sf(data = tracts19, colour= NA, aes(fill = q5(medianage)), showlegend = TRUE) +
  scale_fill_manual(values = palette6,
                   labels = qBr(tracts19, "medianage"),
                   name = "Median Age") +
  geom_sf(data = boulder.sf, aes(colour = q5(price)), show.legend = "point", size = .5) +
  scale_color_manual(values = palette5,
                   labels = qBr(boulder.sf, "price"),
                   name = "Median Age\n(Quintile Breaks)") +
  labs(title="Median Age per Neighborhood (Tract) and Home Prices",
       #subtitle="Light grey line is a 0.5mi buffer to have sense of scale of distance from amenities"
       ) +
  mapTheme()

```

## Exploratory Analysis: Correlation Plots

The Exploratory Analysis here helped us understand which variables (internal and external; numeric or categorical) are positively correlated to price change. 

### Correlation Matrix

```{r Corr Matrix, message=FALSE, warning=FALSE, paged.print=FALSE, echo=FALSE}

corrplot <- st_drop_geometry(boulder.sf) %>% 
  select(price, Size, TotalBathrooms, TotalBedrooms, GarageSize, MedHHInc, pctWhite, medianage, parks_nn1, trails_nn1, schools_nn1, libraries_nn1, university_nn1, healthcare_nn1, restaurant_nn1, marijuanaestablishments_nn1, floodzones, sceniccorridor) %>% na.omit(na.action = "omit")

ggcorrplot(
  round(cor(corrplot), 1), 
  p.mat = cor_pmat(corrplot),
  show.diag = TRUE,
  colors = c("#8d2323", "white", "#ddaa88"),
  type="lower",
  insig = "blank") +  
    labs(title = "Correlation across numeric variables")

corrplot2 <- st_drop_geometry(boulder.sf) %>% 
  select(price, Size, TotalBathrooms, TotalBedrooms, GarageSize, MedHHInc, pctWhite, medianage, parks_nn1, trails_nn1, schools_nn1, libraries_nn1, marijuanaestablishments_nn1, floodzones, sceniccorridor) %>% na.omit(na.action = "omit")

ggcorrplot(
  round(cor(corrplot2), 1), 
  p.mat = cor_pmat(corrplot2),
  show.diag = TRUE,
  colors = c("#8d2323", "white", "#ddaa88"),
  type="lower",
  insig = "blank") +  
    labs(title = "Correlation across numeric variables, dropping colinearity")

```

### Correlation to Internal Characteristics

```{r Internal Numeric, message=FALSE, warning=FALSE}

#Internal Characteristics Correlation Plots
st_drop_geometry(boulder.sf) %>% 
  mutate(Age = 2015 - YearBuilt) %>%
  dplyr::select(price, Size, Age, TotalBedrooms, TotalBathrooms, GarageSize) %>%
  filter(price <= 1000000, Age < 500) %>%
  gather(Variable, Value, -price) %>% 
  ggplot(aes(Value, price)) +
     geom_point(size = .5) + geom_smooth(method = "lm", se=F, colour = "#FA7800") +
     facet_wrap(~Variable, ncol = 4, scales = "free") +
     labs(title = "Price as a function of continuous variables") +
     plotTheme()

```

Numerical features describing pertaining to house size are positively correlated to price. Age is negatively correlated to price. 

### Correlation to Categorical Variables 

Price as a function of non numeric variables. In the plots above, we see how price increases as age decreases, and how numeric variables are positively correlated to price increase. Looking at non numeric attributes of the home might shed interesting insight for understanding why age is negatively correlated to price. A general assumption here could be that architectural styles in this County are not historically valuable to appraisers. Meaning that age may not add appraising value to a property here in contrast to cities like Washington DC or Philadelphia, for example, which have greater historical valuation. 

```{r Non numeric}

st_drop_geometry(boulder.sf) %>% 
  dplyr::select(price, BuildingType, Quality, Construction, Internal) %>%
  filter(price <= 1000000) %>%
  gather(Variable, Value, -price) %>% 
   ggplot(aes(Value, price)) +
     geom_bar(position = "dodge", stat = "summary", fun.y = "mean", scientific = FALSE) +
     facet_wrap(~Variable, ncol = 2, scales = "free") +
     labs(title = "Price as a function of categorical variables", y = "Mean_Price") +
     plotTheme() + theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

As you can see on the bar plots, categorical variables influence price increase significantly. Building typology, construction, interiority finishes and the quality rate from appraisals determine price strongly. While building type and material might be good features to use in a prediction model, quality should be used cautiously, as there is a level of bias in appraisals that the data may not reflect.

### Correlation to External Features

```{r External Features, echo=TRUE, message=FALSE, warning=FALSE}

#Price as a function external characteristics
st_drop_geometry(boulder.sf) %>% 
  mutate(Age = 2015 - YearBuilt) %>%
  dplyr::select(price, Age, pctWhite, MedHHInc, medianage, parks_nn1, trails_nn1, schools_nn1, restaurant_nn1, university_nn1, healthcare_nn1) %>%
  filter(price <= 1000000, Age < 500) %>%
  gather(Variable, Value, -price) %>% 
  ggplot(aes(Value, price)) +
     geom_point(size = .5) + geom_smooth(method = "lm", se=F, colour = "#FA7800") +
     facet_wrap(~Variable, ncol = 2, scales = "free") +
     labs(title = "Price as a function of continuous variables") +
     plotTheme()

```

### Regressions for determining correlation strength 

The following two regressions test significance of multiple internal features and then several external features we engineered in the previous part of this exercise.


```{r Model 1: Internal Features Only, echo=TRUE, message=FALSE, warning=FALSE}

head(boulder.sf)

reg1 <- lm(price ~ ., data = st_drop_geometry(boulder.sf) %>% 
                                 dplyr::select(price, Size, YearBuilt, 
                                               Construction, BuildingType, Internal, Quality,
                                               TotalBedrooms, TotalBathrooms
                                               ))
summary(reg1)

reg1 %>%
  tidy() %>%
  kable(
    caption = "Coefficient-Level Estimates for a Model Fitted to Predict Home Prices in 
    Boulder County", 
    col.names = c("Predictor", "Estimate", "Std.Err", "t-stat", "p-value"), 
    digits = c(0, 2, 3, 2, 3),
    align = c("l", "r", "r", "r", "r")
  ) %>%
  kable_styling() %>%
  footnote(general = "Adjusted R-squared:  0.3781")

```


```{r Model 2: Internal + Demographic Characteristics}

reg2 <- lm(price ~ ., data = st_drop_geometry(boulder.sf) %>% 
                                 dplyr::select(price, Size, YearBuilt, 
                                               Construction, BuildingType, Internal, Quality,
                                               TotalBedrooms, TotalBathrooms, MedHHInc, pctWhite,
                                               medianage))
summary(reg2)


reg2 %>%
  tidy() %>%
  kable(
    caption = "Coefficient-Level Estimates for a Model Fitted to Predict Home Prices in 
    Boulder County", 
    col.names = c("Predictor", "Estimate", "Std.Err", "t-stat", "p-value"), 
    digits = c(0, 2, 3, 2, 8),
    align = c("l", "r", "r", "r", "r")
  ) %>%
  kable_styling() %>%
  footnote(general = "Adjusted R-squared:  0.3799")

```

The above model shows how including demographic features such as HH Income, Population, Age and Race add greater significance to the overall regression.

```{r Model 3: Internal + Demographics + Amenities}

reg3 <- lm(price ~ ., data = st_drop_geometry(boulder.sf) %>% 
                                 dplyr::select(price, Size, YearBuilt, 
                                               Construction, BuildingType, Internal, Quality, 
                                               TotalBedrooms, TotalBathrooms, MedHHInc,
                                               pctWhite, medianage, parks_nn1,
                                               schools_nn1, libraries_nn1, trails_nn1,
                                               marijuanaestablishments_nn1, 
                                               floodzones, sceniccorridor))

summary(reg3)

reg3 %>%
  tidy() %>%
  kable(
    caption = "Coefficient-Level Estimates for a Model Fitted to Predict Home Prices in 
    Boulder County", 
    col.names = c("Predictor", "Estimate", "Std.Err", "t-stat", "p-value"), 
    digits = c(0, 2, 3, 2, 8),
    align = c("l", "r", "r", "r", "r")
  ) %>%
  kable_styling() %>%
  footnote(general = "Adjusted R-squared:  0.4396")

```

When adding many external features and amenities (ie, parks, schools, libraries and trails, etc), the adjusted r-squared value is telling us that 50% of the variables in this list could be statistically significant to price. 


## Training the Model for homeprice predictions

In this section and forward in the document, we use the featured engineered data set for the housing data and split it into two groups: a training set and a test set. 

```{r}
#----Training vs test set----

bouldert.sf <- filter(boulder.sf, toPredict==0)

inTrain <- createDataPartition(
              y = paste(bouldert.sf$Size, bouldert.sf$YearBuilt, bouldert.sf$TotalBedrooms), 
              p = .75, list = FALSE)

boulder.training <- bouldert.sf[inTrain,] 
boulder.test <- bouldert.sf[-inTrain,]  

reg.training <- lm(price ~ ., data = st_drop_geometry(boulder.training) %>% 
                                    dplyr::select(price, Size, YearBuilt, 
                                               Construction, BuildingType, Internal, Quality, 
                                               TotalBedrooms, TotalBathrooms, MedHHInc,
                                               pctWhite, medianage, parks_nn1,
                                               schools_nn1, libraries_nn1, trails_nn1,
                                               marijuanaestablishments_nn1, 
                                               floodzones, sceniccorridor))

boulder.test <-
  boulder.test %>%
  mutate(Regression = "Baseline Regression" ,
         price.Predict = predict(reg.training, boulder.test),
         price.Error = price.Predict - price,
         price.AbsError = abs(price.Predict - price),
         price.APE = (abs(price.Predict - price)) / price.Predict)%>%
  filter(price < 5000000)


#----MAE----
mean(boulder.test$price, na.rm = T)
mean(boulder.test$price.AbsError, na.rm = T)
  

#----MAPE----
mean(boulder.test$price.APE, na.rm = T)
  #model errors by 27%

#----Generalizability----
fitControl <- trainControl(method = "cv", number = 100)
set.seed(825)

reg.cv <- 
  train(price ~ ., data = st_drop_geometry(bouldert.sf) %>% 
                                dplyr::select(price, Size, YearBuilt, 
                                               Construction, BuildingType, Internal, Quality, 
                                               TotalBedrooms, TotalBathrooms, MedHHInc,
                                               pctWhite, medianage, parks_nn1,
                                               schools_nn1, libraries_nn1, trails_nn1,
                                               marijuanaestablishments_nn1, 
                                               floodzones, sceniccorridor),
        method = "lm", trControl = fitControl, na.action = na.pass)

reg.cv
reg.cv$resample[1:5,]

#Table for MAE and MAPE
st_drop_geometry(boulder.test) %>%
    summarize(MAE = mean(price.AbsError, na.rm = T),
              MAPE = mean(price.APE, na.rm = T)) %>%
    kable() %>% kable_styling()

#Predicted prices as a function of observed prices
st_drop_geometry(boulder.test) %>%
  ggplot(aes(price.Predict, price), na.rm=TRUE) +
     geom_point(size = .5) + geom_smooth(method = "lm", se=F, colour = "#b5838d") +
     labs(title = "Predicted Prices as a function of Observed Prices",
          x = "Predicted Price", y = "Observed Price",
          caption="Figure XX") +
     plotTheme()
```


```{r}
#-----Map of predicted prices w/ Entire Dataset----
boulder.sf <-
  boulder.sf %>%
  mutate(Regression = "Baseline Regression",
         price.Predict = predict(reg.training, boulder.sf))
ggplot() +
    geom_sf(data=tracts19, show.legend = NA, color='grey', lwd=0.1, alpha=.4)+
    geom_sf(data=boulderCounty, show.legend = NA, fill = "transparent", lwd=0.8)+
    geom_sf(data = boulder.sf, aes(color = q5(price.Predict)), 
            show.legend = "point", size = 0.3)+
    scale_color_brewer(type=seq, palette = "palette10", labels=qBr(boulder.sf,"price.Predict"),
                      name="Quintile\nBreaks")+
    labs(title="Predicted Prices for All Homes",
         subtitle="Boulder County, CO", 
         caption="Figure XX") +
    mapTheme()

#Cross validation
#Generalizability
fitControl <- trainControl(method = "cv", number = 100)
set.seed(825)

reg.cv <- 
  train(price ~ ., data = st_drop_geometry(bouldert.sf) %>% 
                                dplyr::select(price, Size, YearBuilt, 
                                               Construction, BuildingType, Internal, Quality, 
                                               TotalBedrooms, TotalBathrooms, MedHHInc,
                                               pctWhite, medianage, parks_nn1,
                                               schools_nn1, libraries_nn1, trails_nn1,
                                               marijuanaestablishments_nn1, 
                                               floodzones, sceniccorridor), 
     method = "lm", trControl = fitControl, na.action = na.pass)

reg.cv
reg.cv$resample[1:5,]

#Distribution of MAE
ggplot(data=reg.cv$resample, aes(reg.cv$resample$MAE)) + 
  geom_histogram(color="#08519c", fill="#08519c", alpha=0.5, bins=50) +
  geom_vline(data=boulder.test, aes(xintercept= mean(price.Error)), color="#b5838d", linetype="dashed") +
  labs(title = "Distribution of Mean Absolute Error: Baseline Regression",
       subtitle = "k-fold cross validation; k=100",
       x = "Mean Absolute Error", y = "Count",
       caption="Figure XX") +
  plotTheme()
```

#Moran's I
```{r message=FALSE, warning=FALSE, paged.print=FALSE, echo=FALSE}
moranTest <- moran.mc(boulder.test$price.Error, 
                      spatialWeights.test, nsim = 999)

#Observed and permuted Moran's I
ggplot(as.data.frame(moranTest$res[c(1:999)]), aes(moranTest$res[c(1:999)])) +
  geom_histogram(binwidth = 0.01) +
  geom_vline(aes(xintercept = moranTest$statistic), colour = "#FA342A",size=1) +
  scale_x_continuous(limits = c(-1, 1)) +
  labs(title="Observed and permuted Moran's I",
       subtitle= "Observed Moran's I in orange",
       x="Moran's I",
       y="Count",
       caption="Figure XX") +
  plotTheme()
  
#Price as a function of 
  st_drop_geometry(boulder.test) %>%
  ggplot(aes(lagPriceError, price.Error), na.rm=TRUE) +
     geom_point(size = .5) + geom_smooth(method = "lm", se=F, colour = "#08519c") +
     labs(title = "Price Error as a function of the Spatial Lag of Price Errors",
          caption="Figure XX",
          x="Spatial Lag of Price Errors (Mean Error of 5 Nearest Neighbors)",
          y="Price Error") +
     plotTheme()
```



## Map of Predicted Prices: Entire Dataset

```{r Map Price Predict}

boulder.test$price.Predict<- predict(boulder.training, newdata = boulder.test)

feature <- c("toPredict = 0", "toPredict = 1")
names(feature) <- c(0,1)

price.Predict <- ggplot() + 
  geom_sf(data = boulder,fill = "grey90") +
  geom_sf(data = boulder.s,aes(color = q5(Predicted.Price)),size = .5) +
  scale_color_manual(values = palette5,
                     labels = qBr(boulder.s,'Predicted.Price'),
                     name = "Price, $") +
  facet_wrap(~as.factor(toPredict),
             labeller = labeller(toPredict = feature)) +
  labs(title = 'Map of Predicted Sale Price\n',
       subtitle = '',
       caption = 'Figure RESULT 7') +
  mapTheme() + 
  plotTheme()

predicted.price

```



## Testing model accuracy: Price predictions by Census Tracts

The tracts effects accounts for the mean of prices if the values from price to prediction are equal, meaning that other categorical features might be good for price prediction. 

Summary of reg.tracts will indicate if census tracts is highly significant here. 

```{r Model Tracts}
reg.tracts <- lm(price ~ ., data = as.data.frame(boulder.training) %>% 
                                  dplyr::select(price, Size, YearBuilt, 
                                               Construction, BuildingType, Internal, Quality, 
                                               TotalBedrooms, TotalBathrooms, MedHHInc,
                                               pctWhite, medianage, parks_nn1,
                                               schools_nn1, libraries_nn1, trails_nn1,
                                               marijuanaestablishments_nn1, 
                                               floodzones, sceniccorridor))
                
stargazer(reg.tracts, type="html", star.cutoffs = c(0.05, 0.01, 0.001), 
          median=TRUE, title="Tracts Regression Results of Training Set", align=TRUE,
          single.row=TRUE, digits=2, omit = c())
          
summary(reg.tracts) %>% 
  tidy() %>%
  kable(align='l', caption="Variables in Training Set Neighborhood Regression", 
        digits=2) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "300px")          


#----baseline error vs neighborhood effects----
boulder.test.tracts <-
  boulder.test %>%
  mutate(Regression = "Census Tracts Effects",
         price.Predict = predict(reg.tracts, boulder.test),
         price.Error = price.Predict- price,
         price.AbsError = abs(price.Predict- price),
         price.APE = (abs(price.Predict- price)) / price) %>%
  filter(price < 5000000)

bothRegressions <- 
  rbind(
    dplyr::select(boulder.test, starts_with("price"), Regression, GEOID),
    dplyr::select(boulder.test.tracts, starts_with("price"), Regression, GEOID)) 

st_drop_geometry(bothRegressions) %>%
  group_by(Regression) %>%
  summarize(MAE = mean(price.AbsError, na.rm = T),
            MAPE = mean(price.APE, na.rm = T),
            Error = mean(price.Error, na.rm = T)) %>%
  kable() %>% kable_styling()

```



```{r Model Tracts Both Regressions}

#----MAP of mean MAPE by tracts for bothRegressions----
st_drop_geometry(bothRegressions) %>%
  group_by(Regression, GEOID) %>%
  summarize(mean.MAPE = mean(price.APE, na.rm = T)) %>%
  ungroup() %>% 
  left_join(tracts19) %>%
    st_sf() %>%
    ggplot() + 
      geom_sf(aes(fill = mean.MAPE)) +
      geom_sf(data = bothRegressions, colour = "black", size = .5) +
      geom_sf(data = tracts19, fill = "transparent") +
      facet_wrap(~Regression) +
      scale_fill_gradient(low = palette5[1], high = palette5[5],
                          name = "MAPE", limits = c(0,1)) +
      labs(title = "Mean test set MAPE by neighborhood") +
      mapTheme()


#----MAPE as a function of price----
st_drop_geometry(bothRegressions) %>%
  gather(Variable, Value, -Regression, -GEOID) %>%
  filter(Variable == "price.APE" | Variable == "price") %>%
  group_by(GEOID, Variable) %>%
    summarize(meanValue = mean(Value, na.rm = T)) %>%
    spread(Variable, meanValue) %>%
    ggplot(aes(price.APE, price), na.rm=TRUE) +
     geom_point(size = 2, color="#e5989b") + 
     #geom_smooth(method = "lm", se=F, colour = "#FA7800") +
     labs(title = "Mean Absolute Percentage Error (MAPE) as a function of Price",
          x="MAPE by Neighborhood",
          y="Mean Price by Neighborhood") +
     plotTheme()

```

### Generalizability by Neighborhood

```{r Generalizability Tracts}

summary(tracts19$MedHHInc)

#Determining High Income vs Low Income
census <- tracts19 %>% 
  mutate(incomeContext =ifelse(MedHHInc > mean(MedHHInc,na.rm = T), "High Income", "Low Income")) %>%
  select(incomeContext)

#Generalizability by Neighborhood
ggplot() + geom_sf(data = census, aes(fill = incomeContext)) +
    scale_fill_manual(values = c("#ffcdb2", "#b5838d"), name="Income Context") +
    labs(title = "Income Context",
         subtitle="Boulder County, CO") +
    mapTheme()

```

## Discussion

```{r}

```




## Conclusion

```{r}

```





